---
title: "Homework 3"
author: "Alexis"
date: "10/7/2019"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(p8105.datasets)
library(dplyr)
library(patchwork)
library(viridis)
library(ggplot2)


knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
  )

  options(
    ggplot2.continuous.colour = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  
  scale_colour_discrete = scale_colour_viridis_d
  scale_fill_discrete = scale_fill_viridis_d
  
  theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

## Problem 1
The goal is to do some exploration of this dataset. To that end, write a short description of the dataset, noting the size and structure of the data, describing some key variables, and giving illstrative examples of observations. Then, do or answer the following (commenting on the results of each):

```{r}
data("instacart")
```

There are `r nrow(instacart)` total observations in this dataset of `r n_distinct(pull(instacart, user_id))` unique users and `r ncol(instacart)` variables. Character variables include `eval_set`, `product_name`, `aisle`, and `department`, and the rest of the variables in the dataset are numeric. The average hour of the day that each product was ordered was hour `r instacart %>% pull(order_hour_of_day) %>% mean`, while the median day of the week of each product was ordered was day `r instacart %>% pull(order_dow) %>% median`. 

Example:
Order id #1 has a user id of 112108 and this was their fourth order on Instacart. They ordered this at 10am and ordered eight products such as Bulgarian Yogurt and organic celery hearts. We can also determine the department and aisle from which each product came from. We can also tell it's been 9 days since their previous order.

```{r}
instacart %>%
  filter(order_id == 1)
```

* How many aisles are there, and which aisles are the most items ordered from?

There are `r n_distinct(pull(instacart, aisle_id))` aisles. The aisles most items are ordered from are fresh vegetables, fresh fruits, and packaged vegetables fruits


```{r}
instacart %>%
  count(aisle) %>%
  arrange(desc(n))
```

* Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>%
  group_by(aisle) %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  ggplot(aes(x = reorder(aisle, n), y = n)) +
  geom_point() +
  labs(
    title = "Items Ordered in Aisles",
    x = "Aisle",
    y = "Number of Items"
    ) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
```

* Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>%
  filter(aisle == c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  select(product_name, aisle) %>%
  group_by(aisle) %>%
  count(product_name) %>%
  arrange(desc(n, aisle)) %>% 
  top_n(3, n) %>% 
  rename(
    Aisle = aisle, Product = product_name, Number = n) %>%
  knitr::kable()
```

* Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table)


```{r}
instacart %>%
  filter(
      product_name == c("Pink Lady Apples", 
                        "Coffee Ice Cream")) %>%
  select(
    order_dow, order_hour_of_day, product_name) %>%
  group_by(
    product_name, order_dow) %>%
  summarize(
    mean_hour = mean(order_hour_of_day)) %>%
     mutate(
      order_dow =
        recode(order_dow, 
            "0" = "Sunday" , "1" = "Monday",
            "2" = "Tuesday", "3" = "Wednesday",
            "4" = "Thursday", "5" = "Friday",
            "6" = "Saturday"),
    mean_hour = round(mean_hour, digits = 2)) %>%
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour) %>%
  rename(
    Product = product_name) %>%
  knitr::kable()
```

## Problem 2
This problem uses the BRFSS data. DO NOT include this dataset in your local data directory; instead, load the data from the p8105.datasets package.

```{r}
data("brfss")
```

First, do some data cleaning:
* format the data to use appropriate variable names;
* focus on the “Overall Health” topic
* include only responses from “Excellent” to “Poor”
* organize responses as a factor taking levels ordered from “Poor” to “Excellent

```{r}
clean_brfss =
  brfss_smart2010 %>%
  janitor::clean_names() %>%
   filter(
     topic == "Overall Health") %>%
  rename(
    county = "locationdesc",
    state = "locationabbr",
    resp_id = "respid") %>%
  mutate(
    county = 
      gsub(".*-", "", county, perl = TRUE),
    response = 
      factor(response, 
             levels = c("Poor", "Fair", "Good",
                        "Very good", "Excellent"),
             ordered = TRUE)
  ) 
```

Using this dataset, do or answer the following (commenting on the results of each):

* In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
clean_brfss %>%
  filter(year == 2002) %>%
  group_by(state) %>%
  summarize(
    locations = n_distinct(county)
  ) %>%
  filter(locations >= 7) %>%
  arrange(desc(locations)) %>%
  knitr::kable()
```


```{r}
clean_brfss %>%
  filter(year == 2010) %>%
  group_by(state) %>%
  summarize(
    locations = n_distinct(county)
  ) %>%
  filter(locations >= 7) %>%
  arrange(desc(locations)) %>%
  knitr::kable()
```

In 2002, 6 states were observed at 7 or more locations: Pennslyvania, Massachusetts, New Jersey, Connecticut, Florida, and North Carolina. In 2010, 14 states were observed at 7 or more locations: Florida, New Jersey, Texas, California, Maryland, North Carolina, Nebraska, Washington, Massachusetts, New York, Ohio, Colorado, Pennslyvania, and South Carolina. From 2002 to 2010, the number of states observed at 7 or more locations more than doubled. 


* Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).


```{r}
clean_brfss %>%
  filter(response == "Excellent") %>%
  group_by(year, state) %>%
  mutate(
    avg_data_value = mean(data_value)) %>%
  select(year, state, avg_data_value) %>%
  
    ggplot(aes(x = year, y = avg_data_value, color = state)) +
  geom_line() +
  labs(
    title = "Average Data Value over Time",
    x = "Years",
    y = "Average Data Value"
    ) +
  theme(legend.position = "none") 

```

From the spaghetti graph, we can see that average data value is pretty volatile but within the range of 0-30.

* Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State 


```{r}
clean_brfss %>%
  filter(
    state == "NY", 
    year == c("2006", "2010")) %>% 

 
  select(year, response, data_value) %>%
   ggplot(aes(x = response, y = data_value, color = year)) +
  geom_boxplot() +
     facet_grid(~year) +
  labs(
    title = "Distribution of data-value for 
    Responses in NYS",
    x = "Response",
    y = "Data Value"
    ) +
  theme(legend.position = "none") 
   
```
We can see from the two box plots that they both follow patterns of movement between response categories. It appears 2010 had higher data values. In both years, "good" and "very good" responses seemed to elicit the highest data values.

## Problem 3

* Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).

```{r}
accel_data = read_csv("./data/accel_data.csv") %>%
  janitor::clean_names() %>%
  rename(day_of_week = "day") %>%
   pivot_longer(
    activity_1:activity_1440,
   names_to = "activity_number",
    values_to = "activity_counts") %>% 
  mutate(
    activity_number = 
      gsub(".*_", "", activity_number, perl = TRUE))
```


* Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

* Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph





